---
title: RADPAD Mixed Model
output: pdf_document
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(tidyverse)
library(Matrix)
library(lme4)
library(lmerTest)
library(emmeans)
library(knitr)
```

```{r echo = FALSE}
radpad <- read_csv("radpad.csv") |>
  mutate(ID = as.factor(ID)) |>
  mutate(RADPAD = as.factor(`RADPAD Drape Used? Y/N`)) |>
  mutate(Occupation = as.factor(Occupation)) |>
  mutate(Procedure = as.factor(`Procedure  type (BPV, PDA PMI, PV Stent)`))
```

### Mixed Model

I used a log transform on the response to improve the model fit (by inspection of residual plots). The random effect is procedure ID.

```{r}
m <- lmer(log(Dose + 1) ~ RADPAD*Occupation + (1 | ID), data = radpad)
```

### ANOVA for Fixed Effects

```{r}
anova(m)
```

### LS Means for RADPAD by Occupation

LS means have been back-transformed from log scale.

```{r}
emmeans(m, ~ RADPAD | Occupation, type = "response")
```

### Pairwise contrasts for RADPAD by Occupation

Contrasts have been back-transformed from log scale.

```{r}
rg <- ref_grid(m)
em <- emmeans(regrid(rg, transform = "response"), ~ RADPAD | Occupation)
c <- contrast(em, interaction = "pairwise")
summary(c, infer = c(TRUE, TRUE))
```

\newpage

### Residual Analysis

```{r out.width = "50%", out.height = "50%"}
mdat <- data.frame(predicted = predict(m), residual = residuals(m))
ggplot(mdat, aes(x = residual)) + geom_histogram() +
  labs(title = "Residuals")
ggplot(mdat,aes(sample=residual)) + stat_qq() + stat_qq_line() +
  labs(title = "QQ Plot")
```


